Optimal Peak Shaving with Bifacial Solar PV: Simulated Storage Battery Dispatch for Electric Vehicle Charging Load

### 2024-01-10 Paper/paper.tex
couple last sonia edits

\begin{equation}
  \label{eq:cost}
  \begin{split}
    C_m           & = \sum_k^K [p_{p,k,m}  max(SL^+_{k,m})] + \sum_k^K [p_{e,k,m} \sum (SL^+_{k,m}\Delta t) ] \\
                  & \text{where:}                                                                             \\
    SL_{k,m}^+(t) & = SL(t) \forall SL(t)>0 \text{ in TOU period $k$ and month $m$}                           \\
    C_m           & \in \mathbb{R}^+ [\$] \text{ is total retail electric cost for month}\ m\                 \\
    p_{p,k,m}     & \in \mathbb{R}^+ [\$/kW] \text{ is power price for TOU period}\ k\ \text{and month}\ m\   \\
    p_{e,k,m}     & \in \mathbb{R}^+ [\$/kWh] \text{ is energy price for TOU period}\ k\ \text{and month}\ m\ \\
    K             & \in \mathbb{Z}^+ \text{ is the number of TOU periods} \\
    \Delta t      & = 0.25 [h] \\
  \end{split}
\end{equation}

@@

\begin{equation}
  \label{eq:optimization}
  \begin{split}
    min[C_m(B_c,B_d)] & = min[C_m(T_1,T_2,..T_K)]                                                                          \\
                      & s.t.                                                                                               \\
    B_c(t)            & \le B_{c,max}                                                                                      \\
    B_d(t)            & \le B_{d,max}                                                                                      \\
    SOC_{min}         & \le SOC \le SOC_{max}                                                                              \\
                      & \text{where:}                                                                                      \\
    T_k               & \in \mathbb{R}^+ [kW] \text{ is threshold for}\ k\text{-th TOU period of}\ K\ \text{total periods} \\
    SOC(t)            & \in \mathbb{R}^+ \le 1 [kWh/kWh]  \text{ is battery state of charge timeseries}\                   \\
  \end{split}
\end{equation}

>>>>

\begin{equation}
  \label{eq:cost}
  \begin{split}
    C_m           & = \sum_k^K [p_{p,k,m}  max(SL^+_{k,m})] + \sum_k^K [p_{e,k,m} \sum (SL^+_{k,m}\Delta t) ] \\
                  & \text{where:}                                                                             \\
    SL_{k,m}^+(t) & = SL(t) \forall SL(t)>0 \text{ in TOU period $k$ and month $m$}                           \\
    C_m           & \in \mathbb{R}^+ (\$) \text{ is total retail electric cost for month}\ m\                 \\
    p_{p,k,m}     & \in \mathbb{R}^+ (\$/kW) \text{ is power price for TOU period}\ k\ \text{and month}\ m\   \\
    p_{e,k,m}     & \in \mathbb{R}^+ (\$/kWh) \text{ is energy price for TOU period}\ k\ \text{and month}\ m\ \\
    K             & \in \mathbb{Z}^+ \text{ is the number of TOU periods} \\
    \Delta t      & = 0.25 h \\
  \end{split}
\end{equation}

@@

\begin{equation}
  \label{eq:optimization}
  \begin{split}
    min[C_m(B_c,B_d)] & = min[C_m(T_1,T_2,..T_K)]                                                                          \\
                      & s.t.                                                                                               \\
    B_c(t)            & \le B_{c,max}                                                                                      \\
    B_d(t)            & \le B_{d,max}                                                                                      \\
    SOC_{min}         & \le SOC \le SOC_{max}                                                                              \\
                      & \text{where:}                                                                                      \\
    T_k               & \in \mathbb{R}^+ (kW) \text{ is threshold for}\ k\text{-th TOU period of}\ K\ \text{total periods} \\
    SOC(t)            & \in \mathbb{R}^+ \le 1 (kWh/kWh)  \text{ is battery state of charge timeseries}\                   \\
  \end{split}
\end{equation}
